17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-05-27 rules/rules22.tex
remove todo
Change script names for proof track.

The limits for \paralleltrack{} and \cloudtrack{} are available at \hb{check}
\url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.

@@

\header{Time Limit.}
This track will use a wall-clock time limit of 20 minutes per solver/benchmark
pair. The time limit for checking the satisfying assignment is yet to be
determined, but is anticipated to be around 5 minutes of wall-clock time per
solver.

@@

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two scripts
with their solver.  The first script,
\texttt{starexec\_solver\_default}, should take the name of the benchmark file as
a single argument and run the solver on the benchmark.
%
As described in Section~\ref{sec:logistics}, the benchmark
will contain the commands \akey{(check-sat)} and \akey{(get-proof)}.
%
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

@@

\header{Input/Output Checker.}
The second script, \texttt{starexec\_checker\_default}, should take
the benchmark file name as first argument and the stdout output of the
solver script as second argument.  Note that this output will
usually start with the \texttt{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

@@

\header{Wrapper and Post-Processor.}
Solvers in this track will be wrapped in the competition to include the script
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_default}}, which calls the solver and checker script.
The track will use
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
as a post-processor
to validate and accumulate the results.

>>>>

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2022/parallel-and-cloud-tracks.html}.

@@

\header{Time Limit.}
This track will use a wall-clock time limit of 20 minutes per solver/benchmark
pair. The time limit for checking the satisfying assignment is yet to be
determined, but is anticipated to be around 15 minutes of wall-clock time.

@@

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two scripts
with their solver.  The first script,
\texttt{smtcomp\_solver}, should take the name of the benchmark file as
a single argument and run the solver on the benchmark.
%
As described in Section~\ref{sec:logistics}, the benchmark
will contain the commands \akey{(check-sat)} and \akey{(get-proof)}.
%
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

@@

\header{Input/Output Checker.}
The second script, \texttt{smtcomp\_checker}, should take
the benchmark file name as first argument and the stdout output of the
solver script as second argument.  Note that this output will
usually start with the \texttt{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

@@

\header{Wrapper and Post-Processor.}
Solvers in this track will be wrapped in the competition to include the script
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_proof}}, which calls the solver and checker script.
The track will use
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
as a post-processor
to validate and accumulate the results.
